
\documentclass[11pt]{extarticle}
\usepackage{times}

\begin{document}
\title{Study Report}
\author{Sean Soderman\\
      \and
      Josh Smith
}
\date{\today}
\maketitle

\section*{Problem Identification}
Participants were able to fulfill the tasks outlines by the scenarios. The most common error was not being able to
find the title box on the review page. A similar problem occured when users submitted the review without a title
and were not notified that their submission was invalid. The image upload button was also too small and|or ambiguous
for the user to find. They would also try to create a review by clicking their profile page's review section
header. When one of the "blind" participants attempted to register an account with a name that already existed,
a very confusing error occured. Also, the top bar of the website was pushed down by an overly long username. This
caused it to obscure the title form of the review page, further obfuscating it.
\section*{Prioritization}
\begin{itemize}
\item Registration error.
\item Title box finding when submitting review.
\item Submitting review without title error message omission.
\item Long usernames pushing down top bar.
\item Ambiguous image upload button
\item Profile page 'Review' section hovering.
\end{itemize}
\section*{Theorization: Reasons}
\begin{itemize}
\item Registration error: user name isn't checked against existing users.
\item Title box finding when submitting review: It's not centered over body form.
\item Submitting review without title error message omission: We don't check.
\item Long usernames pushing down top bar: The username text is pushing down other elements.
\item Ambiguous image upload button: It is quite small and tightly grouped near the avatar \& karma count.
\item Profile page 'Review' section hovering: We asked them to review something and since they were already on their
profile page, this was the first thing they went to.
\end{itemize}

\section*{Theorization: Solutions}
\begin{itemize}
\item Registration error: check user name against existing users.
\item Title box finding when submitting review: Center the title box.
\item Submitting review without title error message omission: Check for lack of form info in title.
\item Long usernames pushing down top bar: Truncate the username.
\item Ambiguous image upload button: Make icon larger, put it on the side of the avatar.
\item Profile page 'Review' section hovering: No solution.
\end{itemize}

\section*{Successes}
\begin{itemize}
\item All tasks were accomplished.
\item Users could easily find the search bar
\item Users could also easily discover the about me edit button.
\item Log in and register buttons were located in intuitive locations.
\end{itemize}

\section*{Uncertainty}
We need actual blind people to participate in the study. The screen reader was difficult for sighted users to
use. 
\end{document}
