%"Study_Script.tex", by Sean Soderman
%Script for study
\documentclass[11pt]{extarticle}
\usepackage{times}

\begin{document}
\title{Study Design}
\author{Sean Soderman\\ 
        \and
        Dylan Soderman
}
\date{\today}
\maketitle

\section*{Script}
\begin{itemize}
   \item Basic greeting
      \begin{itemize}
      \item How are you?
      \item I appreciate that you could participate in this study.
      \end{itemize}
\end{itemize}
\begin{itemize}
   \item Introduce Josh
      \begin{itemize}
      \item This is Josh. He will be taking some notes during the test.
      \end{itemize}
\end{itemize}
\begin{itemize}
   \item Describe what we're doing
      \begin{itemize}
      \item We are designing an interface for a review website.
      \item It should help people review games and find games.
      \item We are interested in what you think of the design so far.
      \item We are recording information for analysis purposes only.
      \item We do expect to modify the design.
      \end{itemize}
\end{itemize}
\begin{itemize}
   \item Describe the scenarios the user should fulfill
\end{itemize}
\subsection*{Scenarios}
   \subsubsection*{Create a profile}
      You have just heard about the cool new website for all your game review needs, DjangoFett, and wanted
      to start up a profile on the website. It would be most satisfying to have a fully customized profile.
      You would like to be one of the first people to write a review on this
      website. You have in mind a recent game you recognize.
   \subsubsection*{Finding games}
      Upon finishing your review, you wanted to check if the game Little Big Planet 2 had many reviews, since it is
      rather popular. You are now wondering if there is a game that has at least more than 1 review
      on the website. You let one of the reviewers know whether you agree or disagree with an up/down vote
      and comment.
\begin{itemize}
\item Make sure the user knows what he or she needs to know. Clarify the instructions if needed.
\end{itemize}
\end{document}
